Effects of CHILDREN's programs

### 2020-02-26 paper.Rnw
clarification of which models we want

Questions:\\
effect of\\
- healthy meals (DGE criterion) on healthy characteristics\\
- real meals subsidy on number of meals\\
- real trips subsidy on number of trips\\
- real meals subsidy on self-worth and day-to-day skills\\
- real trips subsidy on self-worth and day-to-day skills\\

@@

\begin{equation}
\label{Meals Grants Regression Model}
  y_{it} = \beta_0 + \beta_1 x_{it} + \epsilon_{it}
\end{equation}

@@

Where: 
y: Health outcomes: lessIll, dietaryKnowledge,  appreciateHealthy
x: DGECriteria Number

@@

Where: 
y: Equal Opportunity proxies: selfworth, dayToDaySkills
x: Real Lunch grant, real Trips grant
<<ChanceEqualityRegressions, echo=FALSE, results='asis', message=FALSE>>=

@@

\{Ehrenwörtliche Erklärung aller Teilnehmer}

>>>>

Questions:\\
effect of\\
- healthy meals (DGE criterion) standardized on healthy characteristics standardized, with eatersPerMeal as weights\\
- real meals subsidy on number of meals\\
- real trips subsidy on number of trips\\
- real meals subsidy per beneficiary on standardized self-worth and standardized day-to-day skills\\
- real trips subsidy per beneficiary on standardized self-worth and standardized day-to-day skills\\

@@

@@

@@

<<ChanceEqualityRegressions, echo=FALSE, results='asis', message=FALSE>>=

@@

\section{Ehrenwörtliche Erklärung aller Teilnehmer}
